\Title

### 2022-08-31 rebuttal.tex

%!TeX TS-program = Lualatex
%!TeX encoding = UTF-8 Unicode
%!TeX spellcheck = en-US
% https://tex.stackexchange.com/questions/354194/how-to-edit-newlfm 
\documentclass[9pt]{article}

\usepackage{charter,graphicx}
\usepackage[margin=1in]{geometry}

\usepackage{fancyhdr}
\pagestyle{fancy}

\newcommand{\AuthorAG}{Antoine Grimaldi}
\newcommand{\AuthorCB}{Camille Besnainou}
\newcommand{\AuthorHL}{Hugo Ladret}
\newcommand{\AuthorLP}{Laurent U Perrinet}
\newcommand{\EmailLP}{laurent.perrinet@univ-amu.fr}
\newcommand{\EmailAG}{antoine.grimaldi@univ-amu.fr}
\newcommand{\EmailHL}{hugo.ladret@univ-amu.fr}
\newcommand{\orcidLP}{0000-0002-9536-010X}
\newcommand{\orcidHL}{0000-0001-7999-3751}
\newcommand{\orcidAG}{0000-0002-3107-4788}
\newcommand{\Address}{Institut de Neurosciences de la Timone (UMR 7289); Aix Marseille Univ, CNRS; Marseille, France}%
\newcommand{\Affiliation}{Institut de Neurosciences de la Timone (UMR 7289); Aix Marseille Univ, CNRS;}%
\newcommand{\CityLP}{Marseille, France}%
\newcommand{\WebsiteLP}{https://laurentperrinet.github.io}%

\renewcommand{\headrulewidth}{.4pt}% Default header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
\fancyhf{}% Clear header/footer
\fancypagestyle{plain}{
  \renewcommand{\headrulewidth}{0pt}% No header rule
  \renewcommand{\footrulewidth}{.4pt}% Default footer rule
  \fancyhf{}% Clear header/footer
}
\AtBeginDocument{\thispagestyle{plain}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.5\baselineskip plus 1pt minus 1pt}
%: %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Journal}{IEEE International Conference on Image Processing}%

\bibliography{biblio}

\begin{document}

\hrulefill

\vspace{.1\baselineskip}

\begin{tabular}[b]{@{} l @{}}
  \today\\[12pt] % Date

\AuthorAG\ \\

\Address\\%[6pt]
%\AuthorA\\[6pt]
%%    \AddressA
%    \LongAddressA
%        \phonefrom{\PhoneA}
  Email: \EmailAG %\\[6pt]

\end{tabular}
%\hfill
%\begin{tabular}[t]{@{} l @{}}
%  Mrs. Jane Smith \\ % Addressee of the letter above the to address
%  Recruitment Officer \\ % To address
%  The Corporation \\
%  123 Pleasant Lane \\
%  City, State 12345
%\end{tabular}
%\hspace*{7em}

\hrulefill

\vspace{1\baselineskip}

To the Area Chair of \emph{\Journal},%

\vspace{2\baselineskip}

We would like to thank the reviewers for their comments that help us improve the clarity of our short paper. We are thankful to the reviewers for their global interest and the positive feedbacks raised by our study. %Even if some reviewers explicitly mention their lack of knowledge in the field preventing them to provide a confident evaluation, reviews are encouraging. 
We report in this rebuttal three main remarks brought by reviewers: 1/ about the pertinence of the contribution of this work to the image processing field (0357), 2/ about the clarity of the description of our model and about the figure illustrating it (1B91) and 3/ about the generalization of this model to more realistic data (1B91).

First, we would like to highlight the fact that our work is to be presented at the Special Session about \textit{Neuromorphic and perception-based image acquisition and analysis}. Thus, using as a visual signal the output of an event-based camera fits the scope of this session. This is why we convert motion clouds movies into spikes. We are mostly ready to make some modifications to the manuscript to improve this description. We strongly believe such event-based algorithms will benefit the image processing community.

Second, we will improve the formalism and the figure to clarify some confusing points. From the question, we understand there is some confusion about the scale of Figure 2-(a) and (c). Figure 2-(c) is the spiking output of the layer of hetero-synaptic delays neurons with the raster plot in Figure 2-(a) as input. Indeed, the output spike could not happen before the integration of the whole spatio-temporal motif.

Third, the reviewer points to a really interesting question about generalization, and we would clearly like to go into this direction. Our future goal is to apply this model for more realistic data, and preliminary results are encouraging. As it stands, our model may not be able to infer a velocity that is different from the 8 motion directions learned during training. Indeed, we use a softmax activation function, which implies some lateral inhibition of the neurons of a layer. By changing the spiking mechanism, we believe that this model will be able to infer a linear combination of the basis motion directions learned to generalize to a continuum of motions.

We hope these points clarify our contribution. Thank you for your consideration,
\vspace{\baselineskip}

Sincerely,

\vspace{2\baselineskip}

On behalf of the authors, \\
\AuthorAG

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{.5\baselineskip}
\begingroup
\renewcommand{\section}[2]{}%
%\printbibliography
\endgroup
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-08-31 Grimaldi-etal-BiolCybernetics.tex
premier draft

% !TeX TS-program = Lualatex
% !TeX encoding = UTF-8 Unicode
% !TeX spellcheck = en
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
% CONF: https://2022.ieeeicip.org/
% dates: https://2022.ieeeicip.org/important-dates/
% paper kit: https://cmsworkshops.com/ICIP2022/papers/paper_kit.php#Templates
% actual submission : https://cmsworkshops.com/icip2022/Papers/Submission.asp
% 4 pages + one of references
%Review #0357
%*General Comments to Authors*
%This paper proposes a model for detection of temporal spiking motifs, which can potentially improve the performance of spiking neural networks (SNN). The topic is out of my research scope. However, I am not sure how this paper is related to ICIP. The authors applied the proposed model in motion detection. Such motion is captured by imaging or not? The overall presentation of the paper is acceptable, but I would suggest the authors to more explicitly represent the contribution of the proposed model and how it is expected to benefit image processing studies.
%-----------
%Review #1B91
%*General Comments to Authors*
%The authors propose a Spiking Neural Network-like method that consists of a single layer of spiking neurons aiming to learn the heterosexual-synaptic delays in order to detect motion. The learning happens in a supervised way as the authors transform the Motion Cloud dataset into spike trains in order to control the direction of motion which is the ground-truth information. The authors considered 8 different directions of motion that are assigned to the 8 learnt kernels they introduce in their model. According to the experimental results, the model is able to capture the direction of motion which is evident to the selectivity along the specific axes of the different kernels. Last but not least, The authors assess their model in terms of the classification accuracy as a function of the computational cost. They show that on the one hand, their method is able to highly reduce the computational load by thresholding some of the weights but at the same time achieve the same performance to computationally more greedy algorithms. The paper is very interesting and promising as this method can be easily extended to hardware.
%Some suggestions to improve the presentation of the results are given below:
%1. Figure 2 is a bit confusing. First of all, in (b) it's not that evident the different size of the radius but in few cases - maybe another example could be selected. In addition, if (a)-(b) and (c) is a single experiment how the delay is related to the time we observe the spike trains? Maybe that could be better explained in the text too.
%Last but not least, are these 8 directions enough to capture every motion? Could we use this model in real data or the computational cost would increase as one should consider much higher number of motion directions and as a results much larger set of kernels to be trained?

@@

\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

@@

\usepackage[usenames,dvipsnames]{xcolor} %The package starts from the basic facilities of the color package, and provides easy driver-independent access to several kinds of color tints, shades, tones, and mixes of arbitrary colors.
\usepackage{tcolorbox} % define boxes that can be customed, has to be loaded after xcolor package

@@

\usepackage[switch]{lineno} % add line numbers
\modulolinenumbers[5]

@@

\usepackage%[disable]	% uncomment to hide all the notes
	{todonotes}
\newcommand{\noteAG}[1]{\todo[color=green!40, author=\textbf{Antoine}, inline]{#1}}
\newcommand{\noteLP}[1]{\todo[color=red!20, author=\textbf{Laurent}, inline]{#1}}
\newcommand{\modif}[1]{\todo[color=orange!20, author=\textbf{Proposition}, inline]{#1}}

%\newcommand{\mycaption}[1]{\captionof{figure}{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackage{orcidlink}

%\bibliography{references}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \newcommand{\mycaption}[1]{\caption*{#1}}

\usepackage{titlesec}
% \titlespacing*{<command>}{<left>}{<before-sep>}{<after-sep>}
\titlespacing*{\section}
{0pt}{1.5ex}{0.8ex}
\titlespacing*{\subsection}
{0pt}{0.9ex}{0.4ex}
\titlespacing*{\subsubsection}
{0pt}{0.5ex}{0.3ex}
\titlespacing*{\paragraph}{%
  0pt}{%              left margin
  0.0\baselineskip}{% space before (vertical)
  1em}%               space after (horizontal)

\usepackage{setspace}
%%%-----------------------------------------------------------------
% Title.
% ------
\title{\Title}
%
% Single address.
% ---------------
\name{
\AuthorAG, \AuthorLP
\thanks{\Acknowledgments}
}
\address{\Affiliation}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
\Abstract
\end{abstract}
%
\begin{keywords}
\Keywords
\end{keywords}
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{abeles1982role}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.

@@

\activeweights^\postsynaddr(t) = \{\synapticweight_\ranksyn^\postsynaddr | \presynaddr_\arank = \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + \synapticdelay_\ranksyn^\postsynaddr\}_{\arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]}

@@

Pr(k=\postsynaddr \; | \; \timev) =

@@

\bibliographystyle{IEEEbib}
\bibliography{references}
\end{document}

>>>>

%!TeX TS-program = pdfLaTeX
%!TeX encoding = UTF-8 Unicode
%!TeX spellcheck = en-US
%!BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%======================================================%%
%% to compile with pdflatex/xelatex use pdflatex option %%
%%======================================================%%

%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
%%\documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
%%\documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
%%\documentclass[default]{sn-jnl}% Default
%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout
\documentclass[iicol]{sn-jnl}

%%%% Standard Packages
%%<additional latex packages if required can be included here>
\usepackage[lofdepth,lotdepth,position=top]{subfig}
\usepackage{tabularx}
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published 
%%%%  by Springer Nature. The guidance has been prepared in partnership with 
%%%%  production teams to conform to Springer Nature technical requirements. 
%%%%  Editorial and presentation requirements differ among journal portfolios and 
%%%%  research disciplines. You may find sections in this template are irrelevant 
%%%%  to your work and are empowered to omit any such section if allowed by the 
%%%%  journal you intend to submit to. The submission guidelines and policies 
%%%%  of the journal take precedence. A detailed User Manual is available in the 
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\jyear{2022}%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

%%\unnumbered% uncomment this for unnumbered level heads%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%\usepackage[usenames,dvipsnames]{xcolor} %The package starts from the basic facilities of the color package, and provides easy driver-independent access to several kinds of color tints, shades, tones, and mixes of arbitrary colors.
%\usepackage{tcolorbox} % define boxes that can be customed, has to be loaded after xcolor package

@@

%\usepackage[switch]{lineno} % add line numbers
%\modulolinenumbers[5]

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\usepackage%[disable]	% uncomment to hide all the notes
%	{todonotes}
%\newcommand{\noteAG}[1]{\todo[color=green!40, author=\textbf{Antoine}, inline]{#1}}
%\newcommand{\noteLP}[1]{\todo[color=red!20, author=\textbf{Laurent}, inline]{#1}}
%\newcommand{\modif}[1]{\todo[color=orange!20, author=\textbf{Proposition}, inline]{#1}}

\begin{document}
%%%-----------------------------------------------------------------
% Title.
% ------
\title{\Title}
%
% Single address.
% ---------------

\author*[1]{\fnm{Antoine} \sur{Grimaldi}}\email{antoine.grimaldi@univ-amu.fr}

\author[2]{\fnm{Amélie} \sur{Gruel}}\email{amelie.gruel@univ-cotedazur.fr}

\author[2]{\fnm{Jean} \sur{Martinet}}\email{jean.martinet@univ-cotedazur.fr}

\author[1]{\fnm{Laurent} \sur{Perrinet}}\email{laurent.perrinet@univ-amu.fr}

\affil[1]{\orgdiv{Department}, \orgname{\Affiliation}, \orgaddress{\street{\Street}, \city{Marseille}, \postcode{13005}, \country{France}}}
\affil[2]{\orgdiv{SPARKS}, \orgname{Université Côte d'Azur, CNRS, I3S}, \orgaddress{\street{2000 Rte des Lucioles}, \city{Sophia-Antipolis}, \postcode{06900}, \country{France}}}

%
%\ninept
%
%
\abstract{\Abstract}
%
\keywords{\Keywords}
%
\maketitle
%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}
%
In 1982, Abeles asked if the role of cortical neurons is whether to integrate synaptic inputs or rather to detect coincidences in temporal spiking patterns~\cite{abeles1982role}. While the first possibility favors the rate coding theory, the second highlights the function of temporal precision in the neural code. Since, numerous studies demonstrated the emergence of synchronicity in the activity within a neural population~\cite{riehle1997spike, davis2021spontaneous}, efficient encoding thanks to the use of spike latencies~\cite{perrinet2004coding, gollisch2008rapid} or precise timing in the auditory system~\cite{deweese2002binary, carr1990circuit}. All these findings, and more~\cite{bohte2004evidence}, highlight the importance of the temporal aspect of the neural code and suggest the existence of repeated spatio-temporal patterns in biological spike trains.

@@

toto
%\activeweights^\postsynaddr(t) = \{\synapticweight_\ranksyn^\postsynaddr | \presynaddr_\arank = \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + \synapticdelay_\ranksyn^\postsynaddr\}_{\arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]}

@@

toto
%Pr(k=\postsynaddr \; | \; \timev) =

@@

\bibliographystyle{apalike}
\bibliography{Grimaldi-etal-BiolCybernetics}
\end{document}
